Independent Component Analysis

### 2022-04-29 paper.tex
add outlines

\section{Applications}
3) example: sound single decomposition
4) tock price
5) EGG

>>>>

\section{Applications}
1) sklearn example
3) example: sound single decomposition
4) stock price
5) EEG
% (https://towardsdatascience.com/independent-component-analysis-ica-a3eba0ccec35)

\section{How to check the robustness and }

1) check if the performance matrix is identity (Te-won Lee, p. 51)
\begin{align}
W A &= I.
\end{align}

2) check how fast w changes (ICA_projectionPursuit1612.05445.pdf, p. 12)

\section{PCA vs. ICA}
% (https://www.cs.ubc.ca/~jnutini/documents/mlrg_pca.pdf)

\section{what if two of the sources are dependent}
s3 = signal.sawtooth(2*np.pi*time) # saw tooth signal
s4 = s1 + s2
s5 = s1 - s2
